Caribou Demographic Projection - interesting & informative title TBD

### 2022-12-07 analysis/paper/paper.Rmd
explanation of priors in progress
more little notes in paper document

Note alternative exponential survival analysis method - put results in appendix, show it doesn't make much difference.

## Calibrating to results from national model

Explain method for selecting values for remaining priors

Write for now assuming that caribouMetrics paper will be published somewhere.

@@

Table 2. Monitoring scenarios adapted from [@rettie_summary_2017].
```{r}
tbl <- "Years|Initial collars|Min collars|cow multiplier|collaring month|collar duration
3|25|25|3|1|3
"
df <- read.delim(textConnection(tbl),header=FALSE,sep="|",strip.white=TRUE,stringsAsFactors=FALSE)
names(df) <- unname(as.list(df[1,]))
df <- df[-1,] # remove first row
row.names(df)<-NULL
knitr::kable(df)
```
TO DO: fill in set of monitoring scenarios when we have decided what they are.

>>>>

@@

Table 2. Monitoring scenarios adapted from [@rettie_summary_2017].
```{r}
tbl <- "Years|Initial collars|Min collars|cow multiplier|collaring month|collar duration
3|25|25|3|1|3
"
df <- read.delim(textConnection(tbl),header=FALSE,sep="|",strip.white=TRUE,stringsAsFactors=FALSE)
names(df) <- unname(as.list(df[1,]))
df <- df[-1,] # remove first row
row.names(df)<-NULL
knitr::kable(df)
```
TO DO: fill in set of monitoring scenarios when we have decided what they are.
*from Anna: happy to chat about what these could be! (e.g. see suggestions above for examples of other ranges...)
